\input{preamble.tex}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\vspace{1em}
\makeheading{{\head Bryan W.\ Weber}}

\section{{\sectionfont Contact Information}}

% MACROS: \rcolwidth is the width of the right column of the table
%             (adjust it to your liking; default is 1.85in).
%         \ccolwidth is width of area between left and right boxes.
%
\newlength{\rcolwidth}
\setlength{\rcolwidth}{2.5in}%
\newlength{\ccolwidth}
\setlength{\ccolwidth}{1pt}
\newlength{\lcolwidth}
\setlength{\lcolwidth}{\textwidth-\rcolwidth-\ccolwidth}
%
% Address box
\begin{varwidth}{\lcolwidth}%
Department of Mechanical Engineering\\
University of Connecticut\\
191 Auditorium Road U-3139\\
Storrs, CT 06269 USA%
\end{varwidth}%
\hfill
%Vertical rule separating address from other contact info.
\begin{varwidth}{\ccolwidth}
\rule{0.5pt}{4\baselineskip} %Comment this line to remove the line.
\end{varwidth}%
\hfill
% Non-snail-mail contact information
\begin{varwidth}{\rcolwidth}%
\textit{E-mail:} \email{weber@engr.uconn.edu}\\
\textit{Work:} +1-860-486-8043 \\
\textit{Cell:} +1-412-443-6447 \\
\textit{Web:} \href{http://bryanwweber.com}{bryanwweber.com}
\end{varwidth}%

\section{{\sectionfont Research Interests}}

My research interests lie in developing tools to apply fundamental
combustion insights to solve engineering problems. My recent work
involves developing experimental methods to analyze intermediate species
at practical combustion conditions. I am also interested in developing
methods to analyze computational models, particularly kinetic models of
combustion.

\section{{\sectionfont Education}}

Ph.D., Mechanical Engineering, University of Connecticut, 2014

M.S., Mechanical Engineering, University of Connecticut, 2010

B.S.E., Aerospace Engineering, Case Western Reserve University, 2009

\section{{\sectionfont Professional Experience}}

\position{Visiting Assistant Professor}, \org{University of Connecticut} \hfill 2014--Present

\begin{innerlist}
\item[] Conducting research on the combustion kinetics of alternative and traditional fuels.
\item[] Teaching undergraduate courses in thermal-fluids engineering.
\item[] Mentoring undergraduate students in the capstone design project.
\end{innerlist}

\vspace{\baselineskip}

\position{Contributing Developer}, \org{Cantera} \hfill 2014--Present

\begin{innerlist}
    \item Contributing source code to the open-source software toolkit for chemical kinetics, thermodynamics, and transport processes
    \item Assisting users with usage of Cantera in the online support group
    \item Contributions available on GitHub: \url{https://github.com/Cantera/cantera}
\end{innerlist}

\vspace{\baselineskip}

\position{Graduate Research Assistant}, \org{University of Connecticut} \hfill 2009--2014\\
\position{Undergraduate Research Assistant}, \org{Case Western Reserve University} \hfill 2007--2009\\
\href{http://combdiaglab.engr.uconn.edu}{Combustion Diagnostics Laboratory} --- Director: C.J.\ Sung

\begin{innerlist}
\item[] Conducted experimental and computational studies of the ignition
properties of several alternative fuels and foundational fuels, with
a focus on engine-relevant conditions.
\item[] Designed a species sampling apparatus for time-resolved
species measurements in the rapid compression machine, using gas
chromatography/mass spectrometry to identify and quantify
combustion intermediates.
\item[] Analyzed kinetic models of combustion to determine the parameters
controlling prediction of ignition delay and to improve the ability of
the models to predict combustion events.
\end{innerlist}

\section{{\sectionfont Journal Publications}}

\begin{bibmune}
\item E.E.\ Dames, A.S.\ Rosen, \meauthor{B.W.\ Weber}, C.W.\ Gao,
      C.J.\ Sung, and W.H.\ Green. \papertitle{A Detailed Combined
      Experimental and Theoretical Study on Dimethyl Ether/Propane
      Blended Oxidation.} Under review at Combustion and Flame, 2015.

\item G.\ Kukkadapu, \meauthor{B.W.\ Weber}, and C.J.\ Sung.
      \papertitle{Autoignition study of tetralin in a rapid compression
      machine at elevated pressures and low-to-intermediate temperatures.}
      Fuel, vol.\ 159, pp.\ 436--445, Nov.\ 2015.\\
      \doi{10.1016/j.fuel.2015.06.093}

\item \meauthor{B.W.\ Weber}, C.J.\ Sung, and M.W.\ Renfro. \papertitle{On
        the Uncertainty of Temperature Estimation in a Rapid
        Compression Machine.} Combustion and Flame, vol.\ 162,
        no.\ 6, pp.\ 2518--2528, Jun.\ 2015.
        \doi{10.1016/j.combustflame.2015.03.001}

\item S.M.\ Burke, U.\ Burke, R.\ Mc Donagh, O.\ Mathieu, I.\ Osorio,
        C.\ Keesee, A.\ Morones, E.L.\ Petersen, W.\ Wang, T.A.\ DeVerter,
        M.A.\ Oehlschlaeger, B.\ Rhodes, R.K.\ Hanson, D.F.\ Davidson,
        \meauthor{B.W.\ Weber}, C.J.\ Sung, J.\ Santner, Y.\ Ju, F.M.\ Haas,
        F.L.\ Dryer, E.N.\ Volkov, E.J.\ Nilsson, A.A.\ Konnov, M.\ Alrefae,
        F.\ Khaled, A.\ Farooq, P.\ Dirrenberger, P.A.\ Glaude,
        F.\ Battin-Leclerc, and H.J.\ Curran.\ \papertitle{An Experimental and
        Modeling Study of Propene Oxidation. Part 2: Ignition Delay Time
        and Flame Speed Measurements.} Combustion and Flame, vol.\ 162, no.\ 2,
        pp.\ 296--314, Feb.\ 2015. \parbox{200pt}{\doi{10.1016/j.combustflame.2014.07.032}}

\item \meauthor{B.W.\ Weber}, W.J.\ Pitz, M.\ Mehl, A.C.\ Davis,
        E.J.\ Silke, and C.J.\ Sung. \papertitle{Experiments and
        Modeling of the Autoignition of Methylcyclohexane at High
        Pressure.} Combustion and Flame, vol.\ 161, no.\ 8, pp.\
        1972--1983, Aug.\ 2014.
        \doi{10.1016/j.combustflame.2014.01.018}

\item S.M.\ Sarathy, S.\ Park, \meauthor{B.W.\ Weber}, W.\ Wang,
        P.S.\ Veloo, A.C.\ Davis, C.\ Togbé, C.K.\ Westbrook, O.\ Park,
        G.\ Dayma, Z.\ Luo, M.A.\ Oehlschlaeger, F.N.\ Egolfopoulos,
        T.\ Lu, W.J.\ Pitz, C.J.\ Sung, and P.\ Dagaut. \papertitle{A
        Comprehensive Experimental and Modeling Study of iso-Pentanol
        Combustion.} Combustion and Flame, vol.\ 160, no.\ 12, pp.\
        2712--2728, Dec.\ 2013. \doi{10.1016/j.combustflame.2013.06.022}

\item \meauthor{B.W.\ Weber} and C.J.\ Sung. \papertitle{Comparative
        Autoignition Trends in Butanol Isomers at Elevated Pressure.}
        Energy and Fuels, vol.\ 27, no.\ 3, pp.\ 1688--1698, Mar.\ 2013. \\
        \doi{10.1021/ef302195c}

\item T.\ Tsujimura, W.J.\ Pitz, F.\ Gillespie, H.J.\ Curran,
        \meauthor{B.W.\ Weber}, Y.\ Zhang, and C.J.\ Sung.
        \papertitle{Development of Isopentanol Reaction Mechanism
        Reproducing Autoignition Character at High and Low
        Temperatures.} Energy and Fuels, vol.\ 26, no.\ 8, pp.\ 4871--4886,
        Aug.\ 2012. \doi{10.1021/ef300879k}

\item \meauthor{B.W.\ Weber}, K.\ Kumar, Y.\ Zhang, and C.J.\ Sung.
        \papertitle{Autoignition of n-butanol at elevated pressure and
        low-to-intermediate temperature.} Combustion and Flame,
        vol.\ 158, no.\ 5, pp.\ 809--819, Mar.\ 2011.\\
        \doi{10.1016/j.combustflame.2011.02.005}
\end{bibmune}

\section{{\sectionfont Conference Publications and Presentations}}

\begin{bibmune}
\item G. Kukkadapu (Presenting), \meauthor{B.W. Weber}, and C.J. Sung. \papertitle{Autoignition study
        of tetralin in a rapid compression machines at elevated
        pressures and low-to-intermediate temperatures.}
        Paper 1G05, \ordinalnum{9} US National Technical Meeting of the
        Combustion Institute, Cincinnati, OH, May 2015.

\item K. Kumar (Presenting), J. Bunnell, \meauthor{B.W. Weber}, and C.J. Sung.
        \papertitle{Autoignition of methyl-propanoate
        and a comparison with its selected ester homologs.}
        Paper 1G07, \ordinalnum{9} US National Technical Meeting of the
        Combustion Institute, Cincinnati, OH, May 2015.

\item E.E. Dames (Presenting), \meauthor{B.W. Weber}, A. Rosen, C.W. Gao, C.J. Sung,
        and W.H. Green. \papertitle{Towards a comprehensive DME/propane blended
        combustion kinetic model.}
        Paper 2F16, \ordinalnum{9} US National Technical Meeting of the
        Combustion Institute, Cincinnati, OH, May 2015.

\item S.S.\ Merchant (Presenting), W.H.\ Green, K.M.\ Van Geem, N.
        Hansen, \meauthor{B.W.\ Weber}, and C.J.\ Sung.
        \papertitle{Combustion of the Butanol Isomers: Reaction Pathways
        from High to Low Temperature.} \ordinalnum{8} International
        Conference on Chemical Kinetics, University Seville, Seville,
        Spain, Jul.\ 2013.

\item \meauthor{B.W.\ Weber} (Presenting), W.J.\ Pitz, C.J.\ Sung, M.\ Mehl,
        E.J.\ Silke, and A.C.\ Davis. \papertitle{Experiments and Modeling of
        the Autoignition of Methyl-Cyclohexane at High Pressure.}
        Paper 3A02, \ordinalnum{8} US National Technical Meeting of the
        Combustion Institute, Park City, UT, May 2013.

\item \meauthor{B.W.\ Weber} (Presenting), S.S.\ Merchant, C.J.\ Sung, and W.H.\ Green.
        \papertitle{An Autoignition Study of iso-Butanol: Experiments and
        Modeling.} Paper 3A01, \ordinalnum{8} US National Technical
        Meeting of the Combustion Institute, Park City, UT, May 2013.

\item S.M.\ Sarathy, S.\ Park, W.\ Wang, P.\ Veloo, A.C.\ Davis,
        C.\ Togbé, \meauthor{B.W.\ Weber} (Presenting), C.K.\ Westbrook, O.\ Park,
        G.\ Dayma, Z.\ Luo, M.A.\ Oehlschlaeger, F.\ Egolfopoulos, T.\ Lu,
        W.J.\ Pitz, C.J.\ Sung, and P.\ Dagaut. \papertitle{A Comprehensive
        Experimental and Modeling Study of iso-Pentanol Combustion.}
        Paper 2A12, \ordinalnum{8} US National Technical Meeting of the
        Combustion Institute, Park City, UT, May 2013.

\item \meauthor{B.W.\ Weber} (Presenting) and C.J.\ Sung. \papertitle{Comparative
        Investigation of the High Pressure Autoignition of the Butanol
        Isomers.} Paper A-01, Fall Technical Meeting of the Eastern
        States Section of the Combustion Institute, Storrs, CT, Oct.\
        2011.

\item M.R.\ Harper, W.H.\ Green (Presenting), K.M.\ Van Geem,
        \meauthor{B.W.\ Weber}, C.J.\ Sung, I.\ Stranic, D.F.\ Davidson,
        and R.K.\ Hanson. \papertitle{Combustion of the butanol isomers:
        Reaction pathways at elevated pressures from low-to-high
        temperatures.} Paper \#84, \ordinalnum{7} International
        Conference on Chemical Kinetics, Massachusetts Institute of
        Technology, Cambridge, MA, Jul.\ 2011.

\item \meauthor{B.W.\ Weber} (Presenting) and C.J.\ Sung. \papertitle{A Rapid Compression
        Study of the Butanol Isomers at Elevated Pressure.} Paper 1B13,
        \ordinalnum{7}  US National Technical Meeting of the Combustion
        Institute, Georgia Institute of Technology, Atlanta, GA, Mar.\
        2011.

\item \meauthor{B.W.\ Weber} (Presenting), K.\ Kumar, and C.J.\ Sung.
        \papertitle{Autoignition of Butanol Isomers at Low to Intermediate
        Temperature and Elevated Pressure.} Paper AIAA-2011-0316,
        \ordinalnum{49}  Annual Aerospace Sciences Meeting,
        Orlando, FL, Jan.\ 2011.
\end{bibmune}

\section{{\sectionfont Conference Posters}}

\begin{bibmune}
\item \meauthor{B.W.\ Weber} and C.J.\ Sung. \papertitle{Validation of
        Kinetic Models of the Butanol Isomers At High Pressure
        using a Rapid Compression Machine.} Poster T40,
        \ordinalnum{7} International Conference on Chemical Kinetics,
         Massachusetts Institute of Technology, Cambridge, MA,
         Jul.\ 2011.

\item \meauthor{B.W.\ Weber}. \papertitle{Autoignition of n-Butanol at
        Elevated Pressure and Low to Intermediate Temperature.}
        \ordinalnum{1} Combustion Energy Frontier Research Center
        Annual Meeting, Princeton University, Princeton, NJ,
        Sep.\ 2010.

\item \meauthor{B.W.\ Weber}, K.\ Kumar, and C.J.\ Sung. \papertitle{An
        Investigation of Hydrocarbon Flames using Probe Sampling and
        Gas Chromatography/Mass Spectrometry.} Support of Undergraduate
        Research and Creative Endeavors Symposium and Poster Session,
        Case Western Reserve University, Cleveland, OH, Apr.\ 2009.
\end{bibmune}

\section{{\sectionfont Other Presentations}}

\begin{bibmune}
\item \meauthor{ B.W.\ Weber} and C.J.\ Sung. \papertitle{Analysis of
        Hydrocarbon Fuels using Gas Chromatography/Mass Spectrometry.}
        Summer Undergraduate Research in Energy Sciences Program,
        Dominion Energy East Ohio Branch, Cleveland, OH, Aug.\ 2008.
\end{bibmune}

\vspace{0.1in}

\section{{\sectionfont Teaching Experience}}

\org{University of Connecticut, Storrs, CT, USA}

\vspace{0.25\baselineskip}

\position{Visiting Assistant Professor}
\begin{outerlist}
\item Applied Thermodynamics (scheduled) \hfill Spring 2016
% \begin{innerlist}
%     \item Core course in ME
% \end{innerlist}

\item Fluid Dynamics 1 \hfill Fall 2015
% \begin{innerlist}
%     \item Fundamentals of fluid statics, fluid kinematics, potential flow, viscous flow, integral and differential control volume analysis, and dimensional analysis
%     \item Integrated multi-media content into lecture
%     \item Core course in Mechanical Engineering; 60 third-year undergraduate students
% \end{innerlist}

\item Thermodynamic Principles \hfill Fall 2014, 2015; Spring 2015
\begin{innerlist}
%     \item Taught up to 100 undergraduate students per section from Mechanical, Civil, Biomedical, and Manufacturing Engineering
%     % \item Core course in Mechanical \& other engineering
%     \item Focused on engineering problem solving techniques, including engineering models and logical progression
%     \item Covered First and Second Laws, property evaluation, and nature of entropy
    \item Developed projects involving reports on the generation of property tables, the history of thermodynamics, the importance of cycles, the relation of thermodynamics to other subjects including biology and medicine
%     % \item Evaluated highly, averaging 4.0/5.0 in median overall rating on student evaluations over all semesters
%     % \item Students commented they found the lectures very helpful and that discussion of examples helped with understanding
    \item Supervised 6 teaching assistants
    \item Integrated student participation into lecture via clicker questions
\end{innerlist}

\item Senior Capstone Design Project Mentor \hfill 2014--2015, 2015--2016
\begin{innerlist}
    \item Supervised 5 teams of 2--3 students each in completing capstone design projects
%     \item Complemented the mentorship from industrial sponsors
%     \item Projects included topics in fluid/thermal systems, mechanical design, and mechanics
\end{innerlist}

\item Senior Design Project \hfill Fall 2014, Spring 2015, 2016
\begin{innerlist}
    \item Assisted the primary instructor with administration of the course
    \item Conducted design review meetings with student teams
    \item Evaluated student presentations
\end{innerlist}

\end{outerlist}

\vspace{0.5\baselineskip}

\position{Instructor}
\begin{outerlist}
\item Introduction to Mechanical Engineering \hfill Spring 2012
\begin{innerlist}
    \item Awarded Graduate Teaching Fellowship to participate in this course
    \item Team-taught, multidisciplinary survey course required for all second semester Mechanical Engineering students
\end{innerlist}
\end{outerlist}

\vspace{0.5\baselineskip}

\position{Teaching Assistant}
\begin{outerlist}
\item Combustion for Energy Conversion \hfill Fall 2012
\begin{innerlist}
    \item Presented lecture materials for $\sim$40 upper-level undergraduate students when supervising professor was on travel
    \item Developed and presented four lectures on the fundamentals of combustion modeling and the use of the combustion modeling software
    \item Developed and graded four student projects covering topics of equilibrium, homogeneous reactors, molecular transport, and non-premixed combustion
\end{innerlist}
\end{outerlist}

\section{{\sectionfont Professional Service}}

\begin{lonelist}
\item[] \org{Combustion Energy Frontier Research Center (CEFRC)} \hfill 2012--2014\\
\position{Lead Chair, Junior Associates Committee}

\begin{innerlist}
\item Coordinate monthly teleconferences for graduate students
and post-doctoral researchers in the CEFRC where junior members of
the CEFRC present recent research results to the group.
\item Act as the liaison between the Center's principal investigators
and the junior members.
\end{innerlist}

\item[] \org{U.S.\ Department of Energy} \hfill 2013--2014\\
\position{Member, EFRC Newsletter Editorial Board}

\begin{innerlist}
\item Contribute articles to the Energy Frontier Research Centers (EFRC)
newsletter describing recent scientific advances resulting from
EFRC research, including:\\
\hspace*{0.25in}\href{http://www.energyfrontier.us/newsletter/201210/burning-butanol-better-engine}
{``Burning Butanol in a Better Engine''}\\
\hspace*{0.25in}\href{http://www.energyfrontier.us/newsletter/201401/advantage-renewable-fuels-high-efficiency-engines}
{``The Advantage of Renewable Fuels in High-Efficiency Engines''}\\
\hspace*{0.25in}\href{http://www.energyfrontier.us/newsletter/201404/confined-catalysts-last-longer}
{``Confined Catalysts Last Longer''}
\item Edit articles written by other board members for factual and grammatical correctness.
\end{innerlist}

\item[] Journal Referee
   \begin{innerlist}
       \item Energy \& Fuels
       \item Proceedings of the Combustion Institute
       \item Combustion Science \& Technology
       \item Industrial \& Engineering Chemistry Research
       \item Society of Automotive Engineers World Congress
       \item Measurement
   \end{innerlist}

\end{lonelist}

\section{{\sectionfont Awards and Fellowships}}

Doctoral Dissertation Fellowship, University of Connecticut, 2014

Graduate Predoctoral Fellowship, Department of Mechanical
Engineering, 2013

Graduate Teaching Fellowship, Department of Mechanical Engineering, 2013

Graduate Assistantship in Areas of National
Need, University of Connecticut, 2010

Fred H.\ Vose Prize, Department of Mechanical and
Aerospace Engineering, 2009

Summer Undergraduate Research in Energy Sciences
Grant, Case Western Reserve University, 2008

\section{{\sectionfont Professional Memberships}}
American Chemical Society - Member

American Institute of Aeronautics and Astronautics - Member

American Society of Mechanical Engineers - Member

The Combustion Institute - Member

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
